SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
pass in II

\section{Introduction Remarks}

@@

\section{Source Code Injection on Web Applications}
\label{sec:attacks}

The basic problem behind the most dangerous
web application attacks involves
the absence of input validation. By taking advantage of
this, attackers can inject their code into
applications to perform malicious tasks. Such
an exploit can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.

Bratus et al.~\cite{BLSPS11} portray the issue in a generic fashion:
{\it ``unexpected (and unexpectedly powerful) computational models
  inside targeted systems, which turn a part of the target into a
  so-called `weird machine' programmable by the attacker via crafted
  inputs (a.k.a. `exploits').''} In particular, {\it ``every
  application that copies untrusted input verbatim into an output
  program is vulnerable to code injection.''} Ray and
Ligatti~\cite{RL12b} have proved this claim based on formal language
theory.

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{attack-tree-uml.pdf}
\end{center}
\caption{\label{fig:taxonomy}A taxonomy of source
code injection attacks.}
\end{figure}

Code injection attacks can be divided into two categories. The first
involves binary code and the second source code. An
extensive survey on binary code injection attacks can be found
in reference~\cite{LC03}. Specific advances in exploiting such vulnerabilities
(i.e., ``heap smashing,'' ``arc injection,'' and others) have already
been presented~\cite{PB04} and the countermeasures used to detect such
defects have already been surveyed~\cite{YJP12} (many of them are also
included in a book:~\cite{DKZ12}---Section 13.8). In the present work
we do not include binary code injection, focusing instead on defenses
that protect applications against attacks based on the
source code injection category.

Figure~\ref{fig:taxonomy} presents a taxonomy of source
code injection attacks. Such attacks may involve source code, either of a
{\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
For both categories, we provide examples that will be used
throughout the whole paper.

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of both web and
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying database. This input can
become part of an {\sc sql} query and get executed on the target
database. A code injection attack that exploits the vulnerabilities of
these interfaces by taking advantage of input validation issues like
incorrectly passed parameters or incorrect type handling is called an
{\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}.
Consider a trivial example that takes advantage of incorrectly
filtered quotation characters. In an application that
will send the password for a forgetful user via email by executing the
following query:

@@

\noindent
If an attacker, inputs the string {\tt anything' OR 'x'='x}, he or
she could could obtain the administrator's password by email.
Savvy programmers could use a language's libraries, like {\sc php}'s
{\tt mysql\_real\_escape\_string()} to detect malformed input; or they
could use prepared {\sc sql} statements, instead of statement
templates. Unfortunately,
the increasing number of {\sc sql} injection attacks
suggest that programmers are not always that careful.
By using similar techniques malicious users can perform other exploits based on
{\sc dsl}s like {\sc xp}ath~\cite{SW06,CDL07,MKS09},
{\sc xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
attacks, a malicious user can view sensitive information, destroy or
modify protected data, or even crash the entire application.

{\sc html} is another {\sc dsl} that can be used for malicious purposes
when an application does not properly handle user supplied data. Based
on this vulnerability an attacker can supply valid {\sc html},
typically via a parameter value, and inject their own content into the
page. {\sc html} injection is mainly associated with {\sc xss}
attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
vehicle for an {\sc csrf} attack in the following manner:
Consider a vulnerable bulletin board system where {\tt img} tags are not checked.
A malicious user could embed a {\sc csrf} request within {\tt img}
tags in the following manner:

@@

\noindent
When the page with this injected code is accessed by an administrator,
the attacker (with {\sc id} 13) will gain administrative privileges
while the administrator will have no immediate indication that there
has been an attack.

A recent class of code injection attacks involve dynamic languages
like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
A simple example of a {\sc php} injection attack is an input string
that is fed into an {\tt eval()} function call, e.g., in {\sc php}:

@@

\noindent
The user may pass into the {\tt value} parameter code that will
execute in the server. Hence, if an attacker provides as
input the following string: {\tt 10 ; system(''touch foo'');}
then a file will be created on the server; it is easy
to imagine more detrimental instances.

JavaScript injection attacks, make up a large subset of dynamic
language-driven attacks. Such attacks are manifested when a web
application accepts and redisplays data of uncertain origin without
appropriate validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}. For instance,
consider a web page (foo.net) that prints the value
of a query parameter ({\tt query}) from the
page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject an {\tt iframe} tag
into the page to steal the user's cookie and
send it via an image request to a web site
that he or she controls (malicious.com).
This could be achieved by including the following
link to the malicious web site (or send it via phishing
email) and induce the user to click on it:

\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
\begin{lstlisting}
http://foo.net/vulnerable.html?query=
<iframe src="javascript:document.body.innerHTML=+
'<img src=\"http://malicious.com/?c=
'+encodeURIComponent(document.cookie)+'\">'">
</iframe>
\end{lstlisting}

>>>>

\section{Introduction}

@@

\section{Source Code Injection Attacks\\in Web Applications}
\label{sec:attacks}

The main vulnerability behind the most dangerous
web application attacks involves
the absence of input validation. By taking advantage of
this, attackers can inject their code into
applications to perform malicious tasks. Exploits
of this kind can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.

Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
{\it ``unexpected (and unexpectedly powerful) computational models
  inside targeted systems, which turn a part of the target into a
  so-called `weird machine' programmable by the attacker via crafted
  inputs (a.k.a. `exploits').''} In particular, {\it ``every
  application that copies untrusted input verbatim into an output
  program is vulnerable to code injection.''} Ray and
Ligatti~\cite{RL12b} have proved this claim based on formal language
theory.

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[width=\columnwidth]{attack-tree-uml.pdf}
\end{center}
\caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
language code injection attacks against web applications.}
\end{figure}

Code injection attacks can be divided into two categories. The first
involves binary code and the second higher-level language code. An
extensive survey on binary code injection attacks was conducted by
Lhee and Chapin~\cite{LC03}. Advances in memory corruption vulnerability
exploitation have been studied extensively~\cite{PB04, SPWS13}
and countermeasures to such attacks
have already been surveyed~\cite{YJP12}\cite[Sec. 13.8]{DKZ12}.
In this work
we do not consider binary code injection, focusing instead on defenses
that protect web applications against attacks based on the
injection of higher level language code.

Figure~\ref{fig:taxonomy} presents a taxonomy of source
code injection attacks against web applications.
Such attacks may involve high-level language code, written in either a
{\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
In the following, we briefly discuss examples from both categories
that will be used throughout the paper.

Injection attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s such as {\sc sql} and
{\sc xml} play an significant role in the development of both web and
mobile applications. For example, many applications have interfaces
through which a user enters input to interact with the application,
thereby interacting with the underlying database. This input can
become part of an {\sc sql} query and get executed on the target
database. Code injection attacks that exploit vulnerabilities in database
interfaces by taking advantage of input validation issues, such as
incorrectly passed parameters or incorrect type handling, are called
{\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
Consider a trivial example that takes advantage of incorrectly
filtered quotation characters in an application that
sends a temporary password for a forgetful user via email by executing the
following query:

@@

\noindent
Attackers that would input the string {\tt anything' OR 'x'='x},
could obtain the administrator's password by email.
Savvy programmers can use certain API functions, such as {\sc php}'s
{\tt mysql\_real\_escape\_string()} to detect malformed input, or
better use prepared {\sc sql} statements, instead of statement
templates. Unfortunately,
the increasing number of {\sc sql} injection attacks
suggest that programmers are not always that careful.
Using similar techniques, malicious users can mount other exploits based on
{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09},
{\sc xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
attacks, a malicious user can view sensitive information, destroy or
modify protected data, or even crash the entire application.

{\sc html} is another {\sc dsl} that can be used for malicious purposes
when an application does not properly handle user-supplied data. Based
on this vulnerability attackers can supply valid {\sc html},
typically via a parameter value, and inject their own content into the
page. {\sc html} injection is mainly associated with {\sc xss}
attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
vehicle for cross-site request forgery attacks in the following manner:
Consider a vulnerable bulletin board system where {\tt img} tags are not checked.
A malicious user could embed a {\sc csrf} request within an {\tt img}
tag in the following manner:

@@

\noindent
When the page with this injected code is accessed by an administrator,
the attacker (with {\sc id} 13) will gain administrative privileges,
while the administrator will have no immediate indication that there
has been an attack.

A recent class of code injection attacks involve dynamic languages
such as JavaScript and {\sc php}~\cite{SFVM09,SMS13}.
A simple example of a {\sc php} injection attack is an input string
that is fed into an {\tt eval()} function call, e.g.:

@@

\noindent
The user may pass into the {\tt value} parameter code that will
be executed on the server. Hence, if an attacker provides as
input the following string: {\tt 10 ; system("touch foo");}
then a file will be created on the server---it is easy
to imagine more detrimental scenarios.

JavaScript injection attacks make up a large subset of dynamic
language code injection attacks. Such attacks are enabled when a web
application accepts and redisplays data of uncertain origin without
proper validation and filtering. Based on this flaw, an attacker
can manage to inject a script in the JavaScript engine of a browser
and alter its execution flow~\cite{ELX07}. For instance,
consider a web page that prints the value
of a query parameter ({\tt query}) from the
page's {\sc url} as part of the page's content
without escaping the value. Attackers
can take advantage of this and inject an {\tt iframe} tag
into the page to steal a user's cookie and
send it via an image request to a web site
under their control (malicious.com).
This could be achieved by including the following
link to the malicious web site (or send it via phishing
email) and induce the user to click on it:

\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
\begin{lstlisting}
http://example.com/vulnerable.html?query=
<iframe src="javascript:document.body.innerHTML=+
'<img src=\"http://malicious.com/?c=
'+encodeURIComponent(document.cookie)+'\">'">
</iframe>
\end{lstlisting}
